Fourmile Calibrations

### 2023-02-07 calibration_output.Rmd
added solar rad map

>>>>

## Cumulative solar radiation difference

2011-2020 average of daily station-grid solar rad for DOY 365 (or 366)

```{r cum sol rad, echo = F}

#get rid of a bunch of data
hru_grid_solrad <- hru_grids %>%
  dplyr::select(c(time, ID, solRad)) %>%
  rename(solrad_grid = solRad)

hru_statn_solrad <- hru_statn %>%
  dplyr::select(c(time, ID, solRad)) %>%
  rename(solrad_statn = solRad)

solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('time', 'ID')) %>%
  mutate(diff = solrad_statn - solrad_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>% 
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(solrad_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')

tm_shape(hrus_map_solrad) +
  tm_polygons('solrad_avg_cumdiff', midpoint = NA, palette = 'YlOrRd') +
tm_shape(locations) +
  tm_symbols(col='blue', size=4)
